Object Oriented Shader Composition Using CLOS

### 2018-04-01 els2018-glsl-oop/paper.tex
Minor
Include an image in section 3.

\documentclass{sig-alternate}
\usepackage[english]{babel}
\usepackage{float}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{minted}
\usepackage{hyperref}
\usepackage[all]{hypcap}
\usemintedstyle[glsl]{default}
\usemintedstyle[common-lisp]{default}
\newmintinline[code]{text}{}
\bibliographystyle{unsrt}

@@

\def\abovecaptionskip{1pt}
\def\listingautorefname{listing}

@@

@@

void main(){
  vertex.xyz += vec3(sin(vertex_data.x));
}
\end{minted}
\caption{A fragment shader that warps the vertex position.}
\label{lst:warp}
\end{listing}

@@

void _GLSLTK_main_2(){
  vertex += sin(position.x);
}

@@

The system automatically recognises that the \code{vertex} variable is the same in both shaders and omits the second instance. It also recognises that the \code{position} and \code{vertex_data} variables denote the same input, omits the second declaration, and renames the variable references to match the first declaration. \\

>>>>

\documentclass{sig-alternate}
\usepackage[english]{babel}
\usepackage{float}
\usepackage[labelfont=bf,textfont=md]{caption}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{minted}
\usepackage{hyperref}
\usepackage[all]{hypcap}
\usemintedstyle[glsl]{default}
\usemintedstyle[common-lisp]{default}
\newmintinline[code]{text}{}
\bibliographystyle{unsrt}

@@

@@

\def\abovecaptionskip{1pt}
\def\listingautorefname{listing}
\def\figureautorefname{figure}

@@

void main(){
  vertex.x += sin(vertex_data.y);
}
\end{minted}
\caption{A fragment shader that warps the vertex position.}
\label{lst:warp}
\end{listing}

@@

void _GLSLTK_main_2(){
  vertex.x += sin(position.y);
}

@@

The system automatically recognises that the \code{vertex} variable is the same in both shaders and omits the second instance. It also recognises that the \code{position} and \code{vertex_data} variables denote the same input, omits the second declaration, and renames the variable references to match the first declaration. An example rendering using \autoref{lst:vertex} and \autoref{lst:combined} can be seen in \autoref{fig:regular}. \\

\begin{figure}[h]
  \begin{center}
    \begin{minipage}{.2\textwidth}
      \includegraphics[width=0.9\textwidth]{render-regular.png}
    \end{minipage}
    \begin{minipage}{.2\textwidth}
      \includegraphics[width=0.9\textwidth]{render-warped.png}
    \end{minipage}
  \end{center}
  \caption{Left: rendering of a sphere using \autoref{lst:vertex}. Right: the same with \autoref{lst:warp} added.}
  \label{fig:regular}
\end{figure}
